One more attempt on ArXe

### 2015-12-22 intro.tex
discussion of valence spectra

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay, 
 and 'exchange ICD' for charge transfer contributions to the 
 normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization plays a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

First experiments on ICD in heterogeneous systems were on Ne-Ar 
clusters.\cite{barthnear} Those were followed by studies of 
ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
Pioneering work also showed the 
potential for studies of the interface between a substrate and an 
adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
clusters was recently presented by some of the authors.\cite{
fasshauer2014} For that system, a detailed analysis of 
photoelectron spectra with respect to structural features of the 
mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
fasshauer2014} it was shown that an analysis of the ICD spectra 
allowed to decide between structural alternatives for which the 
photoelectron data were indiscriminate.

Rare gas clusters are suitable prototype systems for studies of
(e.g.) ICD, as they can readily be produced by supersonic 
expansion. Mixed rare gas clusters easily form by coexpansion of 
the two gases through a cooled nozzle. The size of the clusters 
can be changed by varying the expansion parameters, although for 
heterogeneous clusters some uncertainty remains with respect to 
the cluster size, as empirical scaling laws \cite{hagena1981} 
apply to expansion of pure gases only. Early studies of Ar-Xe 
clusters mostly focussed on the extreme cases of a single Xe atom 
embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). 
Different sites of the dopant atom (on top of a surface, 
integrated in an Ar surface, inside the cluster) were 
distinguished by three separate bands in the fluorescence yield 
recorded as a function of excitation wavelength.\cite{lengenprl} 
Increasing the Xe concentration in the expansion lead to changes 
in the fluorescence excitation spectrum that were interpreted as 
formation of \ce{Xe2} and larger Xe complexes inside the clusters.
\cite{lengen} Experiments on Xe-rich mixed clusters were also 
conducted, and concluded that increasing the Xe content in a 
coexpanding ArXe mixture leads to the formation of Xe-core, 
Ar-shell systems with a sharp interface between the two species.\cite
{tchaplyguine,hoener} This finding was confirmed by electron 
diffraction experiments.\cite{Danylchenko} Always, the observed 
Xe content in the clusters is above the Xe content in the 
expanding gas mixture, as Xe can be condensed much easier than Ar.
A complementary study used photoelectron-photoion coincidence of
large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
photoionization significant charge transfer between both species
occurs before the mass spectroscopic final state is reached.\cite{berrah}

Most recently, on the experimental side photoelectron spectra of 
small Ar-Xe clusters were analyzed, adding to the findings in 
earlier work.\cite{Lindblad} We will discuss this paper in 
connection with our results below. Theoretical work on Ar-Xe was 
also published, and had a focus on the radiationless decay of Ar 
inner valence vacancies in these systems.\cite{fasshauer,Fasshauer13}
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system. 
Again, we will detail these results in conjunction with our 
current work.

>>>>

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay, 
 and `exchange ICD' for charge transfer contributions to the 
 normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization plays a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

Rare gas clusters are suitable prototype systems for studies of
ICD, as they can readily be produced by supersonic 
expansion through a cooled nozzle. 
The size of the clusters can be changed by varying the expansion parameters.
The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).

First experiments on ICD in heterogeneous systems used Ne-Ar 
clusters.\cite{barthnear} Those were followed by studies of 
ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
Pioneering work also showed the 
potential for studies of the interface between a substrate and an 
adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
clusters was recently presented by some of the authors.\cite{
fasshauer2014} For this system, a detailed account of the
photoelectron spectra with respect to structural features of the 
mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
fasshauer2014} it was shown that an analysis of the ICD spectra 
allowed to decide between structural alternatives, for which the 
photoelectron data were indiscriminate.

Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
Early work focussed on the fluorescence of a single Xe atom 
embedded in an Ar cluster.\cite{lengenprl}
%Different sites of the dopant atom (on top of a surface, 
%integrated in an Ar surface, inside the cluster) were 
%distinguished by three separate bands in the fluorescence yield 
%recorded as a function of excitation wavelength.\cite{goldberg} 
Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
This finding was confirmed by electron diffraction.\cite{Danylchenko,PhysRevA.76.043202} 
Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,PhysRevA.76.043202}
%A complementary study used photoelectron-photoion coincidence of
%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
%photoionization significant charge transfer between both species
%occurs before the mass spectroscopic final state is reached.\cite{berrah}
%
More recently, photoelectron spectra of 
small Ar-Xe clusters were analyzed, adding to the findings in 
earlier work.\cite{lindblad} We will discuss this paper in 
connection with our results below. 
For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}

A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s\ \citenum{fasshauer,Fasshauer13}.
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system. 
Again, we will detail these results in conjunction with our 
current work.

### 2015-12-22 theo_results.tex
discussion of valence spectra

\begin{table*}[h]

@@

We will now discuss features of several structures, using selected examples.
Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
for the 55 atom core).
Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
%two different argon core sizes one consisting
%of 13 and one consisting of 55 atoms with one xenon atom on one of
%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
%for the 55 atom core). The simulated secondary electron spectra are
%shown in Figure \ref{figure:surf} Panel 1.

>>>>

\begin{table*}[th]

@@

We will now discuss features of several structures, using selected examples.
First we consider cluster having an argon core of 13 and 55 atoms with a single xenon
atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
for the 55 atom core).
Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
%two different argon core sizes one consisting
%of 13 and one consisting of 55 atoms with one xenon atom on one of
%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
%for the 55 atom core). The simulated secondary electron spectra are
%shown in Figure \ref{figure:surf} Panel 1.
